Regression Cube Analysis of Cohort Study Data

### 2015-03-16 draft.tex
first abstract draft

\title{Interactive Visual Regression Cubes Analysis of Image-Centric Cohort Study Data}

@@

%other entries to be set up for journal
\shortauthortitle{Klemm \MakeLowercase{\textit{et al.}}: Interactive Visual Regression Cubes Analysis of Image-Centric Cohort Study Data}
%\shortauthortitle{Firstauthor \MakeLowercase{\textit{et al.}}: Paper Title}

%% Abstract section.
\abstract{%
(The problem).
(New Solution).
(Validation).
(Results).
(Implications).
} % end of abstract

>>>>

\title{Regression Cube Analysis of Cohort Study Data}

@@

%other entries to be set up for journal
\shortauthortitle{Klemm \MakeLowercase{\textit{et al.}}: Regression Cube Analysis of Cohort Study Data}
%\shortauthortitle{Firstauthor \MakeLowercase{\textit{et al.}}: Paper Title}

%% Abstract section.
\abstract{%
\com{Problem}.
Epidemiological studies comprise of heterogenous data about a subject group (a \emph{cohort}) to define disease-specific risk factors.
%%
These data contain information (\emph{features}) about a subjects lifestyle, medical conditions and also medical images of the whole body.
%%
These features are analyzed using statistical regression analyses towards features indicating a disease (the \emph{target feature}).
%%
%These complex data are hard to analyze concurrently, only a few features can be considered in statistical analyses, such as regression analyses.
These analyses usually include two to five features (\emph{independent features}) towards the disease of interest.
\com{New Solution}.
%(New Solution).
We propose a new analyses approach of epidemiological data sets by incorporating all dimensions in a exhaustive regression-based analyses.
%%
It takes all possible combinations of \emph{independent features} towards a \emph{target feature} into account and provides a visualization, which allows for insights into the data by showing relationships possibly unknown to the domain expert.
%%
%The most meaningful features 
A 3D-visualization of all possible combinations of two to three target variables acts as overview over the whole data set.
%%
We call it the \emph{Regression Cube}.
%%
Slicing through the regression cube allows for the detailed analysis of features towards the target disease.
%%
\com{Validation}.
%%
We applied our \emph{Regression Cube} method to a hepatic steatosis data set to reproduce results from a data-mining driven analysis.
%%
We conducted a qualitative analysis with three domain experts on a breast fat data set to derive insights into the correlation between breast lesions and non-image variables.
%%
\com{Results}. TODO.
%%
\com{Implications}.
Epidemiological data sets can for the first time be visually overviewed using a regression-based analysis of all features towards a disease. 
%With our technique it is possible for the first time to provide a overview visualization of variables regarding a target variable.

} % end of abstract
